The Perils of Exploration under Competition: \\ A Computational Modeling Approach

### 2019-05-05 paper/ec19-abstract.tex
Added pointer to the arxiv.
update abstract

\documentclass[format=acmsmall, review=false]{acmart}

\usepackage{acm-ec-19}
\usepackage{tikz} % SW: Added for plots
\usepackage{subfiles}
\usepackage[toc,page]{appendix}
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath,amssymb,amsfonts}
%\usepackage{natbib} % cannot use with AAAI! A.S.

@@

\newcommand{\HMR}{\term{HMR}}
\newcommand{\HM}{\term{HM}}
% a very useful package for edits and comments, from David Kempe (USC)
%\usepackage{color-edits}
\usepackage[suppress]{color-edits}  % use this to suppress the package
\addauthor{as}{red}    % as for Alex
\addauthor{ga}{blue}  % ga for Guy
\addauthor{sw}{orange} % sw for Steven
% e.g. for Alex, provides \asedit{}, \ascomment{} and \asdelete{}.
\setlength{\tabcolsep}{8pt} % Default value: 6pt
\renewcommand{\arraystretch}{1.5} % Default value: 1

@@

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

@@

@@

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\maketitle
\keywords{Multi-armed bandits,Exploration,Competition,Competition vs Innovation}

@@

\xhdr{Discussion.}
Our paper is an experimental counterpart to \cite{CompetingBandits-itcs18}, which considered a similar duopoly model and obtained a number of theoretical results with ``asymptotic" flavor. For analytical tractability, \cite{CompetingBandits-itcs18} makes a somewhat unrealistic simplification that users do not observe any signals about firms' ongoing performance. The strength of competition is varied using assumptions about (ir)rational user behavior. For these reasons, the theorems from \cite{CompetingBandits-itcs18} have no direct bearing on our simulations. However, their high-level conclusion in is an inverted-U relationship similar to ours.

>>>>

\documentclass[acmsmall]{ec19acm}

\settopmatter{printacmref=true}
\fancyhead{}
\copyrightyear{2019} 
\acmYear{2019} 
\setcopyright{rightsretained} 
\acmConference[EC '19]{ACM EC '19: ACM Conference on Economics and Computation}{June 24--28, 2019}{Phoenix, AZ, USA}
\acmBooktitle{ACM EC '19: ACM Conference on Economics and Computation (EC '19), June 24--28, 2019, Phoenix, AZ, USA}
\acmDOI{10.1145/3328526.3329635}
\acmISBN{978-1-4503-6792-9/19/06}

\usepackage{tikz} % SW: Added for plots
\usepackage{subfiles}
\usepackage[toc,page]{appendix}
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath,amssymb,amsfonts}
%\usepackage{natbib} % cannot use with AAAI! A.S.

@@

\newcommand{\HMR}{\term{HMR}}
\newcommand{\HM}{\term{HM}}
% a very useful package for edits and comments, from David Kempe (USC)
%\usepackage{color-edits}
\usepackage{color-edits}  % use this to suppress the package
\addauthor{as}{red}    % as for Alex
\addauthor{ga}{blue}  % ga for Guy
\addauthor{sw}{orange} % sw for Steven
% e.g. for Alex, provides \asedit{}, \ascomment{} and \asdelete{}.
\setlength{\tabcolsep}{8pt} % Default value: 6pt
\renewcommand{\arraystretch}{1.5} % Default value: 1

@@

@@

\titlenote{Extended abstract. Full version is available as a technical report at \url{https://arxiv.org/abs/1902.05590}~.}

@@

  \begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10010405.10010455.10010460</concept_id>
<concept_desc>Applied computing~Economics</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Applied computing~Economics}

\fancyhead{} 
%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\keywords{Multi-armed bandits;Exploration;Competition;Competition vs Innovation}
\maketitle

@@

\gadelete{
\xhdr{Discussion.}
Our paper is an experimental counterpart to \cite{CompetingBandits-itcs18}, which considered a similar duopoly model and obtained a number of theoretical results with ``asymptotic" flavor. For analytical tractability, \cite{CompetingBandits-itcs18} makes a somewhat unrealistic simplification that users do not observe any signals about firms' ongoing performance. The strength of competition is varied using assumptions about (ir)rational user behavior. For these reasons, the theorems from \cite{CompetingBandits-itcs18} have no direct bearing on our simulations. However, their high-level conclusion in is an inverted-U relationship similar to ours.
